---
title: "Task for week 14"
output: Nikolaj Dencker
date: "2024-04-03"


```{r}
library(tidyverse)
library(googlesheets4)
library(leaflet)
```

```{r}
places <- read.csv("CapturingCoordinates - DM2023 (1).csv")
```

```{r}
glimpse(places)
```


# load the coordinates in the map and check: are any points missing? Why?
```{r}
DANmap <- leaflet() %>% 
  addTiles() %>% 
  addMarkers(lng = places$Longitude, 
             lat = places$Latitude,
             popup = places$Description)
```


# Task 2: Read in the googlesheet data you and your colleagues 
# populated with data into the DANmap object you created in Task 1.
```{r}
DANmap
```
# Task 3: Can you cluster the points in Leaflet? Google "clustering options in Leaflet"

```{r}
DANmap_clusters <- leaflet() %>% 
  addTiles() %>% 
  addProviderTiles("OpenStreetMap.France") %>%
  addMarkers(lng = places$Longitude, 
             lat = places$Latitude,
             popup = places$Description,
             clusterOptions = markerClusterOptions())

DANmap_clusters
```

# Task 4: Look at the map and consider what it is good for and what not.

# It provides a good amount of information to the viewer in a short time, but it does lack a certain amount of detail, that
# the previous map was good at showing. 


# Task 5: Find out how to display notes and classifications in the map.
```{r}
DANmap_popups <- leaflet() %>% 
  addTiles() %>% 
  addProviderTiles("OpenStreetMap.France") %>%
  addMarkers(lng = places$Longitude, 
             lat = places$Latitude,
             popup = paste(
             "By:",places$Placename, "<br>",
             "Type:", places$Type,"<br>",
             "Description:", places$description), 
             clusterOptions = markerClusterOptions())
DANmap_popups 
```

